What the hell is the title of this paper?

### 2018-05-12 NIPS 2018/main.tex
Fixed part of the proof

\abs{\max_a Q(s,a) - \mm_a Q(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q(s,a) - \sum_a \pi_{\beta_{\kappa}}(a|s)Q(s,a)}\notag\\ =\ & \abs{\sum_a Q(s,a) \left( \pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q(s,a)} \abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}

@@

where $\pi^*$ is the optimal (deterministic) policy w.r.t. $Q$ and $\pi_{\beta_{\kappa}}$ is the Boltzmann distribution induced by $Q$ with inverse temperature $\beta_{\kappa}$:

@@

\pi_{\beta}(a|s) = \frac{e^{\beta_{\kappa} Q(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q(s,a')}}

@@

Denote by $a_1(s)$ the optimal action for state $s$ under $Q$. We can then write:

@@

\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta_{\kappa} Q(s,a_1(s))}}{\sum_{a'}e^{\beta_{\kappa} Q(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} \left( Q(s,a_1(s)) - Q(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \sum_{a' \neq a_1(s)}e^{\beta_{\kappa} \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}

@@

Combining Eq. \eqref{eq:mm5}, \eqref{eq:mm2}, \eqref{eq:mm3}, and \eqref{eq:mm4}, we obtain:

@@

\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2\gamma R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}

>>>>

\abs{\max_a Q^*(s,a) - \mm_a Q^*(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q^*(s,a) - \sum_a \pi_{\beta_{\kappa}}(a|s)Q^*(s,a)}\notag\\ =\ & \abs{\sum_a Q^*(s,a) \left( \pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q^*(s,a)} \abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}

@@

where $\pi^*$ is the optimal (deterministic) policy w.r.t. $Q^*$ and $\pi_{\beta_{\kappa}}$ is the Boltzmann distribution induced by $Q^*$ with inverse temperature $\beta_{\kappa}$:

@@

\pi_{\beta}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}

@@

Denote by $a_1(s)$ the optimal action for state $s$ under $Q^*$. We can then write:

@@

\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta_{\kappa} Q^*(s,a_1(s))}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} \left( Q^*(s,a_1(s)) - Q^*(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \sum_{a' \neq a_1(s)}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}

@@

Combining Eq. \eqref{eq:mm2}, \eqref{eq:mm3}, and \eqref{eq:mm4}, we obtain:

@@

\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2 R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
Finally, using Eq. \eqref{eq:mm5} we get:
\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)} \leq \frac{2\gamma R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
